---
title: "Lab 00 - Hello IDS!"
author: "Karis McFarlane"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE, warning=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.colous
```{r setup-tibble}
team_data <- tibble(
  name = c("Caitlin", "Karis", "Lena", 
           "Ellie", "John", "Elaine"),
  github_username = c("cb0wman2", "karis-mcfarlane", "lenaartus", 
                      "elliehuntt", "johnwatson-06", "elaine-cyl"), 
  colour = c("powderblue", "maroon", "pink", 
             "blue", "royalblue", "lightpink"),
  hobby = c("Swimming", "Sleeping", "Running", 
            "Cooking", "Tennis", "Travelling"),
  favourite_number = c(7, 3, 22, 16, 10, 11)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
  labs(x = "\n GitHub Username",
       y = "Favourite Number \n",
       title = "Bar Chart") +
   geom_col() +
   scale_fill_identity()
p1
```




### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favourite Number",
          title = "Bar Plot")
```

*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
